---
title: "Assignment_2"
author: "Chi-Yu, Chen"
date: "2018/7/14"
output: pdf_document
---

## 1. Write a program to find the outliers using Box and Whisker’s criterion discussed in the class.

```{r}
outliers <- function(numbers) {
    q1 <- quantile(numbers, 1/4)
    q3 <- quantile(numbers, 3/4)
    iqr <- IQR(numbers)
    return(numbers[numbers <= (q1 - 1.5 * iqr) | numbers >= (q3 + 1.5 * iqr)])
}
x <- c(1,100,120,140,160,180,200,1000)
outliers(x)
```

## 2. Make two vectors:
```{r}
X <- c(1,2,5,10,12)
Y <- c(2,5,1,0,12)
```
##   a. Find the values that are contained in both X and Y.

```{r}
q2.a <- X[X%in%Y]
q2.a
```

##   b. Find values that are in x but not in y and (vice versa).

```{r}
q2.b.xny <- X[!(X%in%Y)]
q2.b.xny
q2.b.ynx <- Y[!(Y%in%X)]
q2.b.ynx
```

##   c. Construct a vector that contains all values contained in either X or Y, and compare this vector to c(X,Y)

```{r}
q2.c <- c(q2.a, q2.b.xny, q2.b.ynx)
q2.c
q2.c.cmp <- c(X,Y)
q2.c.cmp
```

## Load USArrests data set.
## 3. Which states has most and least assault, murder, and rape arrests.

```{r}
data(USArrests)
q3.assault.most <- USArrests[USArrests$Assault==max(USArrests$Assault),]
row.names(q3.assault.most)
q3.assault.least <- USArrests[USArrests$Assault==min(USArrests$Assault),]
row.names(q3.assault.least)
q3.murder.most <- USArrests[USArrests$Murder==max(USArrests$Murder),]
row.names(q3.murder.most)
q3.murder.least <- USArrests[USArrests$Murder==min(USArrests$Murder),]
row.names(q3.murder.least)
q3.rape.most <- USArrests[USArrests$Rape==max(USArrests$Rape),]
row.names(q3.rape.most)
q3.rape.least <- USArrests[USArrests$Rape==min(USArrests$Rape),]
row.names(q3.rape.least) 
```

## 4. Which states are in the bottom 25% of murder and in the top 25% of the murder.

```{r}
q4.muder.q1 <- quantile(USArrests$Murder, 1/4)
q4.murder.lessthanq1 <- row.names(subset(USArrests, Murder < q4.muder.q1))
q4.murder.lessthanq1
```

```{r}
q4.muder.q3 <- quantile(USArrests$Murder, 3/4)
q4.murder.higherthanq3 <- row.names(subset(USArrests, Murder > q4.muder.q3))
q4.murder.higherthanq3
```

## 5. The following function calculates the mean and standard deviation of a numeric vector
```{r}
fn1 <- function(x){
    mean1 <- mean(x)
    sd1 <- sd(x)
    return(mean = mean1, sd = sd1)
}
```
##   Modify the function so that: 
##   a. the default is to use rnorm to generate 30  random normal numbers, and return the standard deviation, 
##   b. if there are missing values, the mean and standard deviation are calculated for the remaining values.
      
```{r}
fn1 <- function(x=rnorm(30)) {
    mean1 <- mean(x, na.rm=TRUE)
    sd1 <- sd(x, na.rm=TRUE)
    return(c(mean=mean1, sd=sd1))
}
x <- c(1,7,2,3,NA,9,5,4,NA)
fn1(x)
```
