---
title: "ass1"
author: "Chi-Yu, Chen"
date: "2018/7/7"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. What are the measures of central tendency and variation of data.

Central tendency: mean, median, mode.
Variation of data: range, variance, standard deviation.


2. What are the different ways to create a vector in R?

```{r}
x2.1 <- 1:5
x2.1
x2.2 <- c(1,2,3,4,5)
x2.2
x2.3 <- c(1:5)
x2.3
x2.4 <- seq(1,5)
x2.4
x2.5 <- seq(1,9,by=2)
x2.5
x2.6 <- seq(1,9,length.out=5)
x2.6
```


3. Create the following vector and check the class 
   ('x','x','x',1,3,5,7,9,2,4,6,8,10)

```{r}
x3 <- c('x','x','x',1,3,5,7,9,2,4,6,8,10)
class(x3)
```


4. Create a vector of positive odd integers less than 100

```{r}
x4 <- seq(1, 100, by=2)
x4
```


5. Remove the values greater than 60 and less than 80

```{r}
x5 <- x4[x4 <= 60 | x4 >= 80]
x5
```


6. Write a function to return standard deviation, mean, and median of the 
   vector from Question 5.

```{r}
calculator <- function(numbers) {
  figures.sd <- sd(numbers)
  figures.mean <- mean(numbers)
  figures.median <- median(numbers)
  return(c(figures.sd,figures.mean,figures.median))
}
x6 <- calculator(x5)
x6
```


7. Create two matrices of the form from the given set of numbers in 
   two ways x1 = {2,3,7,1,6,2,3,5,1} and x2 = {3,2,9,0,7,8,5,8,2}

```{r}
x7.x1 <- matrix(c(2,3,7,1,6,2,3,5,1), 3, 3)
x7.x1
x7.x2 <- matrix(c(3,2,9,0,7,8,5,8,2), ncol=3)
x7.x2
```


8. Find the matrix product

```{r}
x8 <- x7.x1 %*% x7.x2
x8
```


9. Fin the class of 'iris' dataframe, find the class of all the columns of all
   the columns of 'iris' get the summary. Get rownames, get column names. Get 
   the number of rows and the number of columns.

```{r}
class(iris)
class(iris[,1])
class(iris[,2])
class(iris[,3])
class(iris[,4])
class(iris[,5])
str(iris)
rownames(iris)
colnames(iris)
nrow(iris)
ncol(iris)
```


10. Get the last two rows in the last 2 columns from iris dataset.

```{r}
x10 <- iris[(nrow(iris)-1):nrow(iris),(ncol(iris)-1):ncol(iris)]
x10
```

