---
title: "Assignment_3"
author: "Chi-Yu, Chen"
date: "2018/7/26"
output:
  pdf_document: default
  html_document: default
---

## 1. Import the data into R.

```{r}
library(dplyr)
setwd("/Users/ChiYuChen/Data Analysis, Intro/Assignment 3")
forestfires <- read.csv("forestfires.csv")
forestfires
```
## a. How many observations are there in the dataset?
```{r}
q1.a <- nrow(forestfires)
q1.a
```

## b. How many observations are there with a fire (i.e., area>0)
```{r}
q1.b <- filter(forestfires, area>0)
nrow(q1.b)
```
## c. How many observations are there with a rain (i.e., rain>0)
```{r}
q1.c <- filter(forestfires, rain>0)
nrow(q1.c)
```
## d. How many observations are there with both a fire and a rain?
```{r}
q1.d <- filter(forestfires, area>0, rain>0)
nrow(q1.d)
```
## 2. Show the columns month, day, area of the all the observations.
```{r}
q2 <- select(forestfires, month, day, area)
q2
```
## 3. Show the columns month, day, area of the observations with a fire.
```{r}
q3.1 <- filter(forestfires, area>0)
q3.2 <- select(q3.1, month, day, area)
q3.2
```
## 4. How large are the five largest fires (i.e., having largest area)
```{r}
q4.1 <- arrange(forestfires, area)
q4.2 <- tail(q4.1, n=5)
q4.2$area
```
## a. What are the corresponding month, temp, RH, wind, rain area?
```{r}
q4.a <- select(q4.2, month, temp, RH, wind, rain, area)
q4.a
```
## b. Add one column to the data indicating whether a fire occurred for each observation (True for area>0 and False for area ==0)
```{r}
q4.b <- mutate(forestfires, occurred=area>0)
q4.b
```
## 5. Construct a matrix with 10 columns and 10 rows, filled with random numbers between 0 and 1. Apply two different methods.
```{r}
q5.1 <- replicate(10, runif(10)) 
q5.1
q5.2 <- matrix(runif(10*10), ncol=10)
q5.2
```
## a. Calculate the row means of this matrix.
```{r}
q5.a <- rowMeans(q5.2)
q5.a
```
## b. Remake the above matrix, with 100 columns, and 10 rows. Then calculate the column means.
```{r}
q5.b1 <- matrix(runif(100*10), ncol=100)
q5.b2 <- colMeans(q5.b1)
q5.b2
```

